---
title: "ANOVA test for score"
author: Geiser C. Challco <geiser@alumni.usp.br>
comment: ANOVA test to determine whether there were significant differences.
         
         Author - Geiser C. Challco <geiser@alumni.usp.br>
         
         Shiny-Statistic is distributed in the hope that it will be useful,
         but WITHOUT ANY WARRANTY; without even the implied warranty of
         MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
         GNU General Public License for more details.
         
         You should have received a copy of the GNU General Public License.
         This file is  generate using Shiny-Statistic app (https://github.com/geiser/rshinystatistics)
         If not, see <https://www.gnu.org/licenses/>.
output:
  github_document:
    toc: true
  word_document:
    toc: true
  html_document:
    toc: true
fontsize: 10pt
---


```{r setup, include=FALSE}
# Install and Load Packages

if (!'remotes' %in% rownames(installed.packages())) install.packages('remotes')
if (!"rshinystatistics" %in% rownames(installed.packages())) {
  remotes::install_github("geiser/rshinystatistics")
} else if (packageVersion("rshinystatistics") < "0.0.0.9900") {
  remotes::install_github("geiser/rshinystatistics")
}

wants <- c('ggplot2','ggpubr','rshinystatistics','rstatix','utils','randomcoloR')
has <- wants %in% rownames(installed.packages())
if (any(!has)) install.packages(wants[!has])

library(shiny)
library(esquisse)
library(scales)
library(knitr)
library(rmarkdown)

library(utils)
library(ggpubr)
library(ggplot2)
library(randomcoloR)

library(rshinystatistics)
library(rstatix)

library(readxl)
```

```{r}
dat <- read_excel("../data/data.xlsx", sheet = "alunos_ef59")

escolas <- read_excel("../data/data.xlsx", sheet = "escolas")
edat <- merge(dat, escolas, by = "cod_escola", all.x = T)
```


# ANOVA: score ~ time

## Data Preparation

```{r}
data <- edat[,c("aluno_id","ciclo","score")]
data <- data[data$ciclo %in% c("Primeiro Ciclo","Segundo Ciclo"),]
data$ciclo <- factor(data$ciclo, c("Primeiro Ciclo","Segundo Ciclo"))
data <- unique(data)

wdat <- spread(data, ciclo, score)
wdat <- wdat[complete.cases(wdat),]
colnames(wdat) <- c("id","c1","c2")

ldat <- gather(wdat, key = time, value = score, c1,c2) %>%
  convert_as_factor(id, time)
ldat <- rshinystatistics::remove_group_data(ldat, "score", "time", n.limit = 30)
```

## Summary Statistics

```{r}
(sdat <- ldat %>% group_by(time) %>%
   get_summary_stats(score, type = "mean_sd"))
```

```{r, echo=F, purl=F}
kable(sdat, digits = 3)
```

## ANOVA Computation


```{r}
(res.aov <- anova_test(ldat, dv = score, wid = id, within = time))
```

```{r, echo=F, purl=F}
kable(res.aov$ANOVA, digits = 3)
```

```{r, echo=F, purl=F}
kable(res.aov$`Mauchly's Test for Sphericity`, digits = 3)
```

```{r, echo=F, purl=F}
kable(res.aov$`Sphericity Corrections`, digits = 3)
```

## PairWise Computation

```{r}
(pwc <- ldat %>% emmeans_test(score ~ time, detailed = T, p.adjust.method = "bonferroni"))
```

```{r, echo=F, purl=F}
kable(pwc, digits = 3)
```

```{r, dpi=300, fig.width=10, fig.height=6}
pwc <- add_xy_position(pwc, x = "time", fun = "mean_se")
ggline(get_emmeans(pwc), x = "time", y = "emmean", ylab = "score") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  stat_pvalue_manual(pwc, hide.ns = T, tip.length = F)
```



# ANOVA: score ~ time*gender + Error(id/time) 

## Data Preparation

```{r}
data <- edat[,c("aluno_id","gender","ciclo","score")]
data <- data[data$ciclo %in% c("Primeiro Ciclo","Segundo Ciclo"),]
data$ciclo <- factor(data$ciclo, c("Primeiro Ciclo","Segundo Ciclo"))
data <- unique(data)

wdat <- spread(data, ciclo, score)
wdat <- wdat[complete.cases(wdat),]
colnames(wdat) <- c("id","gender","c1","c2")

ldat <- gather(wdat, key = time, value = score, c1,c2) %>%
  convert_as_factor(id, time)
ldat <- remove_group_data(ldat, "score", c("time", "gender"), n.limit = 30)
ldat$gender <- factor(ldat$gender, sort(unique(ldat$gender)))
```

### Check assumptions: Identifying Outliers

```{r}
outliers <- identify_outliers(group_by(ldat, time, gender), score)
(outliers <- outliers[outliers$is.extreme == T,])
```

```{r, echo=F, purl=F}
kable(outliers, digits = 3)
```

### Check assumptions: Normality Test

```{r}
(normality.df <- normality.test.per.groups(ldat, "score", c("time", "gender")))
```

```{r, echo=F, purl=F}
kable(normality.df, digits = 3)
```

```{r}
(non.ids <- unique(do.call(
  c, lapply(which(normality.df$normality == 'NO'), FUN = function(i) {
  idx = which(ldat$time == normality.df$time[i] &
                ldat$gender == normality.df$gender[i])
  getNonNormal(ldat$"score"[idx], ldat$id[idx])
}))))
```

```{r}
if (length(non.ids) > 0)
  ldat2 <- ldat[!ldat$id %in% non.ids,]
```

### Summary Statistics

```{r}
(sdat <- ldat %>% group_by(time, gender) %>%
   get_summary_stats(score, type = "mean_sd"))
```

```{r, echo=F, purl=F}
kable(sdat, digits = 3)
```


```{r}
if (length(non.ids) > 0)
  (sdat <- ldat2 %>% group_by(time, gender) %>%
      get_summary_stats(score, type = "mean_sd"))
```


```{r, echo=F, purl=F}
kable(sdat, digits = 3)
```

## ANOVA Computation

```{r}
(res.aov <- anova_test(ldat, dv = score, wid = id, between = gender, within = time))
```

```{r, echo=F, purl=F}
kable(res.aov$ANOVA, digits = 3)
```

```{r, echo=F, purl=F}
kable(res.aov$`Mauchly's Test for Sphericity`, digits = 3)
```

```{r, echo=F, purl=F}
kable(res.aov$`Sphericity Corrections`, digits = 3)
```

## ANOVA Computation after removing non.normal data


```{r}
if (length(non.ids) > 0)
  (res.aov2 <- anova_test(ldat2, dv = score, wid = id, between = gender , within = time))
```

```{r, echo=F, purl=F}
if (length(non.ids) > 0)
  kable(res.aov2$ANOVA, digits = 3)
```

```{r, echo=F, purl=F}
if (length(non.ids) > 0)
  kable(res.aov2$`Mauchly's Test for Sphericity`, digits = 3)
```

```{r, echo=F, purl=F}
if (length(non.ids) > 0)
  kable(res.aov2$`Sphericity Corrections`, digits = 3)
```


## PairWise Computation

```{r}
(pwc <- ldat %>% group_by(time) %>%
   emmeans_test(score ~ gender, detailed = T, p.adjust.method = "bonferroni"))
```

```{r, echo=F, purl=F}
kable(pwc, digits = 3)
```

```{r}
(emms <- get_emmeans(pwc))
```

```{r, echo=F, purl=F}
kable(emms, digits = 3)
```

```{r, dpi=300, fig.width=10, fig.height=6}
pwc <- add_xy_position(pwc, x = "time", fun = "mean_se", dodge = 0.25)
pd <- position_dodge(width = 0.25)
ggline(emms, x = "time", y = "emmean", color = "gender",
       palette = c("#FF007F","#4D4DFF"),
       position = pd, ylab = "score") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = gender),
                position = pd, width = 0.2) +
  stat_pvalue_manual(pwc, hide.ns = T, tip.length = F, linetype = 1)
```


```{r}
(pwc <- ldat %>% group_by(gender) %>%
    emmeans_test(score ~ time, detailed = T, p.adjust.method = "bonferroni"))
```

```{r, echo=F, purl=F}
kable(pwc, digits = 3)
```

```{r}
(emms <- get_emmeans(pwc))
```

```{r, echo=F, purl=F}
kable(emms, digits = 3)
```



```{r, dpi=300, fig.width=10, fig.height=6}
emms.gg <- emms[which(emms$gender == "Female"),]
if (nrow(emms.gg) > 0)
  ggline(emms.gg, x = "time", y = "emmean", color = "#FF007F", ylab = "score") +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                  width = 0.2, color = "#FF007F") +
    stat_pvalue_manual(
      add_xy_position(pwc[which(pwc$gender == "Female"),],
                      x = "time", fun = "mean_se"),
      hide.ns = T, color = "#FF007F", tip.length = F) +
    labs(title = "gender: Female")+
    theme(legend.text = element_blank())
```


```{r, dpi=300, fig.width=10, fig.height=6}
emms.gg <- emms[which(emms$gender == "Male"),]
if (nrow(emms.gg) > 0)
  ggline(emms.gg, x = "time", y = "emmean", color = "#4D4DFF", ylab = "score") +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                  width = 0.2, color = "#4D4DFF") +
    stat_pvalue_manual(
      add_xy_position(pwc[which(pwc$gender == "Male"),],
                      x = "time", fun = "mean_se"),
      hide.ns = T, color = "#4D4DFF", tip.length = F) +
    labs(title = "gender: Male")+
    theme(legend.text = element_blank())
```



## PairWise Computation after removing non.normal data


```{r}
if (length(non.ids) > 0)
  (pwc2 <- ldat2 %>% group_by(time) %>%
     emmeans_test(score ~ gender, detailed = T, p.adjust.method = "bonferroni"))
```

```{r, echo=F, purl=F}
if (length(non.ids) > 0)
  kable(pwc2, digits = 3)
```

```{r}
if (length(non.ids) > 0)
  (emms2 <- get_emmeans(pwc2))
```

```{r, echo=F, purl=F}
if (length(non.ids) > 0)
  kable(emms2, digits = 3)
```

```{r, dpi=300, fig.width=10, fig.height=6}
if (length(non.ids) > 0) {
  pwc2 <- add_xy_position(pwc2, x = "time", fun = "mean_se", dodge = 0.25)
  pd2 <- position_dodge(width = 0.25)
  
  ggline(emms2, x = "time", y = "emmean", color = "gender",
         palette = c("#FF007F","#4D4DFF"),
         position = pd, ylab = "score") +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = gender),
                position = pd, width = 0.2) +
    stat_pvalue_manual(pwc2, hide.ns = T, tip.length = F, linetype = 1)
}
```


```{r}
if (length(non.ids) > 0)
  (pwc2 <- ldat2 %>% group_by(gender) %>%
     emmeans_test(score ~ time, detailed = T, p.adjust.method = "bonferroni"))
```

```{r, echo=F, purl=F}
if (length(non.ids) > 0)
  kable(pwc2, digits = 3)
```

```{r}
if (length(non.ids) > 0)
  (emms2 <- get_emmeans(pwc2))
```

```{r, echo=F, purl=F}
if (length(non.ids) > 0)
  kable(emms2, digits = 3)
```



```{r, dpi=300, fig.width=10, fig.height=6}
if (length(non.ids) > 0) {
  emms.gg <- emms2[which(emms2$gender == "Female"),]
  if (nrow(emms.gg) > 0)
    ggline(emms.gg, x = "time", y = "emmean", color = "#FF007F", ylab = "score") +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                  width = 0.2, color = "#FF007F") +
    stat_pvalue_manual(
      add_xy_position(pwc[which(pwc$gender == "Female"),],
                      x = "time", fun = "mean_se"),
      hide.ns = T, color = "#FF007F", tip.length = F) +
    labs(title = "gender: Female") +
    theme(legend.text = element_blank())
}
```


```{r, dpi=300, fig.width=10, fig.height=6}
if (length(non.ids) > 0) {
  emms.gg <- emms2[which(emms2$gender == "Male"),]
  if (nrow(emms.gg) > 0)
    ggline(emms.gg, x = "time", y = "emmean", color = "#4D4DFF", ylab = "score") +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                  width = 0.2, color = "#4D4DFF") +
    stat_pvalue_manual(
      add_xy_position(pwc[which(pwc$gender == "Male"),],
                      x = "time", fun = "mean_se"),
      hide.ns = T, color = "#4D4DFF", tip.length = F) +
    labs(title = "gender: Male") +
    theme(legend.text = element_blank())
}
```


# ANOVA: score ~ time*regiao + Error(id/time) 

## Data Preparation

```{r}
data <- edat[,c("aluno_id","regiao","ciclo","score")]
data <- data[data$ciclo %in% c("Primeiro Ciclo","Segundo Ciclo"),]
data$ciclo <- factor(data$ciclo, c("Primeiro Ciclo","Segundo Ciclo"))
data <- unique(data)

wdat <- spread(data, ciclo, score)
wdat <- wdat[complete.cases(wdat),]
colnames(wdat) <- c("id","regiao","c1","c2")

ldat <- gather(wdat, key = time, value = score, c1,c2) %>%
  convert_as_factor(id, time)
ldat <- remove_group_data(ldat, "score", c("time", "regiao"), n.limit = 30)
ldat$regiao <- factor(ldat$regiao, sort(unique(ldat$regiao)))
```

### Check assumptions: Identifying Outliers

```{r}
outliers <- identify_outliers(group_by(ldat, time, regiao), score)
(outliers <- outliers[outliers$is.extreme == T,])
```

```{r, echo=F, purl=F}
kable(outliers, digits = 3)
```

### Check assumptions: Normality Test

```{r}
(normality.df <- normality.test.per.groups(ldat, "score", c("time", "regiao")))
```

```{r, echo=F, purl=F}
kable(normality.df, digits = 3)
```

```{r}
(non.ids <- unique(do.call(
  c, lapply(which(normality.df$normality == 'NO'), FUN = function(i) {
  idx = which(ldat$time == normality.df$time[i] &
                ldat$regiao == normality.df$regiao[i])
  getNonNormal(ldat$"score"[idx], ldat$id[idx])
}))))
```

```{r}
if (length(non.ids) > 0)
  ldat2 <- ldat[!ldat$id %in% non.ids,]
```

### Summary Statistics

```{r}
(sdat <- ldat %>% group_by(time, regiao) %>%
   get_summary_stats(score, type = "mean_sd"))
```

```{r, echo=F, purl=F}
kable(sdat, digits = 3)
```


```{r}
if (length(non.ids) > 0)
  (sdat <- ldat2 %>% group_by(time, regiao) %>%
      get_summary_stats(score, type = "mean_sd"))
```


```{r, echo=F, purl=F}
kable(sdat, digits = 3)
```

## ANOVA Computation

```{r}
(res.aov <- anova_test(ldat, dv = score, wid = id, between = regiao, within = time))
```

```{r, echo=F, purl=F}
kable(res.aov$ANOVA, digits = 3)
```

```{r, echo=F, purl=F}
kable(res.aov$`Mauchly's Test for Sphericity`, digits = 3)
```

```{r, echo=F, purl=F}
kable(res.aov$`Sphericity Corrections`, digits = 3)
```

## ANOVA Computation after removing non.normal data


```{r}
if (length(non.ids) > 0)
  (res.aov2 <- anova_test(ldat2, dv = score, wid = id, between = regiao , within = time))
```

```{r, echo=F, purl=F}
if (length(non.ids) > 0)
  kable(res.aov2$ANOVA, digits = 3)
```

```{r, echo=F, purl=F}
if (length(non.ids) > 0)
  kable(res.aov2$`Mauchly's Test for Sphericity`, digits = 3)
```

```{r, echo=F, purl=F}
if (length(non.ids) > 0)
  kable(res.aov2$`Sphericity Corrections`, digits = 3)
```


## PairWise Computation

```{r}
(pwc <- ldat %>% group_by(time) %>%
   emmeans_test(score ~ regiao, detailed = T, p.adjust.method = "bonferroni"))
```

```{r, echo=F, purl=F}
kable(pwc, digits = 3)
```

```{r}
(emms <- get_emmeans(pwc))
```

```{r, echo=F, purl=F}
kable(emms, digits = 3)
```

```{r, dpi=300, fig.width=10, fig.height=6}
pwc <- add_xy_position(pwc, x = "time", fun = "mean_se", dodge = 0.25)
pd <- position_dodge(width = 0.25)
ggline(emms, x = "time", y = "emmean", color = "regiao",
       palette = c("#0073C2FF","#EFC000FF","#868686FF","#CD534CFF","#7AA6DCFF"),
       position = pd, ylab = "score") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = regiao),
                position = pd, width = 0.2) +
  stat_pvalue_manual(pwc, hide.ns = T, tip.length = F, linetype = 1)
```


```{r}
(pwc <- ldat %>% group_by(regiao) %>%
    emmeans_test(score ~ time, detailed = T, p.adjust.method = "bonferroni"))
```

```{r, echo=F, purl=F}
kable(pwc, digits = 3)
```

```{r}
(emms <- get_emmeans(pwc))
```

```{r, echo=F, purl=F}
kable(emms, digits = 3)
```



```{r, dpi=300, fig.width=10, fig.height=6}
emms.gg <- emms[which(emms$regiao == "Centro-Oeste"),]
if (nrow(emms.gg) > 0)
  ggline(emms.gg, x = "time", y = "emmean", color = "#0073C2FF", ylab = "score") +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                  width = 0.2, color = "#0073C2FF") +
    stat_pvalue_manual(
      add_xy_position(pwc[which(pwc$regiao == "Centro-Oeste"),],
                      x = "time", fun = "mean_se"),
      hide.ns = T, color = "#0073C2FF", tip.length = F) +
    labs(title = "regiao: Centro-Oeste")+
    theme(legend.text = element_blank())
```


```{r, dpi=300, fig.width=10, fig.height=6}
emms.gg <- emms[which(emms$regiao == "Nordeste"),]
if (nrow(emms.gg) > 0)
  ggline(emms.gg, x = "time", y = "emmean", color = "#EFC000FF", ylab = "score") +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                  width = 0.2, color = "#EFC000FF") +
    stat_pvalue_manual(
      add_xy_position(pwc[which(pwc$regiao == "Nordeste"),],
                      x = "time", fun = "mean_se"),
      hide.ns = T, color = "#EFC000FF", tip.length = F) +
    labs(title = "regiao: Nordeste")+
    theme(legend.text = element_blank())
```


```{r, dpi=300, fig.width=10, fig.height=6}
emms.gg <- emms[which(emms$regiao == "Norte"),]
if (nrow(emms.gg) > 0)
  ggline(emms.gg, x = "time", y = "emmean", color = "#868686FF", ylab = "score") +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                  width = 0.2, color = "#868686FF") +
    stat_pvalue_manual(
      add_xy_position(pwc[which(pwc$regiao == "Norte"),],
                      x = "time", fun = "mean_se"),
      hide.ns = T, color = "#868686FF", tip.length = F) +
    labs(title = "regiao: Norte")+
    theme(legend.text = element_blank())
```


```{r, dpi=300, fig.width=10, fig.height=6}
emms.gg <- emms[which(emms$regiao == "Sudeste"),]
if (nrow(emms.gg) > 0)
  ggline(emms.gg, x = "time", y = "emmean", color = "#CD534CFF", ylab = "score") +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                  width = 0.2, color = "#CD534CFF") +
    stat_pvalue_manual(
      add_xy_position(pwc[which(pwc$regiao == "Sudeste"),],
                      x = "time", fun = "mean_se"),
      hide.ns = T, color = "#CD534CFF", tip.length = F) +
    labs(title = "regiao: Sudeste")+
    theme(legend.text = element_blank())
```


```{r, dpi=300, fig.width=10, fig.height=6}
emms.gg <- emms[which(emms$regiao == "Sul"),]
if (nrow(emms.gg) > 0)
  ggline(emms.gg, x = "time", y = "emmean", color = "#7AA6DCFF", ylab = "score") +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                  width = 0.2, color = "#7AA6DCFF") +
    stat_pvalue_manual(
      add_xy_position(pwc[which(pwc$regiao == "Sul"),],
                      x = "time", fun = "mean_se"),
      hide.ns = T, color = "#7AA6DCFF", tip.length = F) +
    labs(title = "regiao: Sul")+
    theme(legend.text = element_blank())
```



## PairWise Computation after removing non.normal data


```{r}
if (length(non.ids) > 0)
  (pwc2 <- ldat2 %>% group_by(time) %>%
     emmeans_test(score ~ regiao, detailed = T, p.adjust.method = "bonferroni"))
```

```{r, echo=F, purl=F}
if (length(non.ids) > 0)
  kable(pwc2, digits = 3)
```

```{r}
if (length(non.ids) > 0)
  (emms2 <- get_emmeans(pwc2))
```

```{r, echo=F, purl=F}
if (length(non.ids) > 0)
  kable(emms2, digits = 3)
```

```{r, dpi=300, fig.width=10, fig.height=6}
if (length(non.ids) > 0) {
  pwc2 <- add_xy_position(pwc2, x = "time", fun = "mean_se", dodge = 0.25)
  pd2 <- position_dodge(width = 0.25)
  
  ggline(emms2, x = "time", y = "emmean", color = "regiao",
         palette = c("#0073C2FF","#EFC000FF","#868686FF","#CD534CFF","#7AA6DCFF"),
         position = pd, ylab = "score") +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = regiao),
                position = pd, width = 0.2) +
    stat_pvalue_manual(pwc2, hide.ns = T, tip.length = F, linetype = 1)
}
```


```{r}
if (length(non.ids) > 0)
  (pwc2 <- ldat2 %>% group_by(regiao) %>%
     emmeans_test(score ~ time, detailed = T, p.adjust.method = "bonferroni"))
```

```{r, echo=F, purl=F}
if (length(non.ids) > 0)
  kable(pwc2, digits = 3)
```

```{r}
if (length(non.ids) > 0)
  (emms2 <- get_emmeans(pwc2))
```

```{r, echo=F, purl=F}
if (length(non.ids) > 0)
  kable(emms2, digits = 3)
```



```{r, dpi=300, fig.width=10, fig.height=6}
if (length(non.ids) > 0) {
  emms.gg <- emms2[which(emms2$regiao == "Centro-Oeste"),]
  if (nrow(emms.gg) > 0)
    ggline(emms.gg, x = "time", y = "emmean", color = "#0073C2FF", ylab = "score") +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                  width = 0.2, color = "#0073C2FF") +
    stat_pvalue_manual(
      add_xy_position(pwc[which(pwc$regiao == "Centro-Oeste"),],
                      x = "time", fun = "mean_se"),
      hide.ns = T, color = "#0073C2FF", tip.length = F) +
    labs(title = "regiao: Centro-Oeste") +
    theme(legend.text = element_blank())
}
```


```{r, dpi=300, fig.width=10, fig.height=6}
if (length(non.ids) > 0) {
  emms.gg <- emms2[which(emms2$regiao == "Nordeste"),]
  if (nrow(emms.gg) > 0)
    ggline(emms.gg, x = "time", y = "emmean", color = "#EFC000FF", ylab = "score") +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                  width = 0.2, color = "#EFC000FF") +
    stat_pvalue_manual(
      add_xy_position(pwc[which(pwc$regiao == "Nordeste"),],
                      x = "time", fun = "mean_se"),
      hide.ns = T, color = "#EFC000FF", tip.length = F) +
    labs(title = "regiao: Nordeste") +
    theme(legend.text = element_blank())
}
```


```{r, dpi=300, fig.width=10, fig.height=6}
if (length(non.ids) > 0) {
  emms.gg <- emms2[which(emms2$regiao == "Norte"),]
  if (nrow(emms.gg) > 0)
    ggline(emms.gg, x = "time", y = "emmean", color = "#868686FF", ylab = "score") +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                  width = 0.2, color = "#868686FF") +
    stat_pvalue_manual(
      add_xy_position(pwc[which(pwc$regiao == "Norte"),],
                      x = "time", fun = "mean_se"),
      hide.ns = T, color = "#868686FF", tip.length = F) +
    labs(title = "regiao: Norte") +
    theme(legend.text = element_blank())
}
```


```{r, dpi=300, fig.width=10, fig.height=6}
if (length(non.ids) > 0) {
  emms.gg <- emms2[which(emms2$regiao == "Sudeste"),]
  if (nrow(emms.gg) > 0)
    ggline(emms.gg, x = "time", y = "emmean", color = "#CD534CFF", ylab = "score") +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                  width = 0.2, color = "#CD534CFF") +
    stat_pvalue_manual(
      add_xy_position(pwc[which(pwc$regiao == "Sudeste"),],
                      x = "time", fun = "mean_se"),
      hide.ns = T, color = "#CD534CFF", tip.length = F) +
    labs(title = "regiao: Sudeste") +
    theme(legend.text = element_blank())
}
```


```{r, dpi=300, fig.width=10, fig.height=6}
if (length(non.ids) > 0) {
  emms.gg <- emms2[which(emms2$regiao == "Sul"),]
  if (nrow(emms.gg) > 0)
    ggline(emms.gg, x = "time", y = "emmean", color = "#7AA6DCFF", ylab = "score") +
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high),
                  width = 0.2, color = "#7AA6DCFF") +
    stat_pvalue_manual(
      add_xy_position(pwc[which(pwc$regiao == "Sul"),],
                      x = "time", fun = "mean_se"),
      hide.ns = T, color = "#7AA6DCFF", tip.length = F) +
    labs(title = "regiao: Sul") +
    theme(legend.text = element_blank())
}
```
